### 2018-03-14 Writing/Thesis/Tex/content/chapter-conclusion.tex
Create Presentation

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding B3L when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable. An effect on the time and quality of predictions for larger data sets would have to be examined still.

>>>>

% Recommendations for future work
\section{Future Work}
\label{sec:conclusion:future}
% More evaluation - meta features
As the results have shown that the approach taken in this thesis has worked out reasonably well, for example when considering the regression-based approach using random forest, many possibilities for additional work arise. An intuitive thought would be to extend the evaluation of the tool, for instance in terms of meta features. Additional sets of meta features could be evaluated, like adding implementations for additional meta features, or considering using only light probing by incorporating the performance values for usually cheap algorithms in the meta features. Since the significant advantage of any approach was lost regarding B3L when moving from the full meta data to the reduced meta data without probing, this might be especially interesting. One could consider adding the meta feature groups for DecisionStump, RandomTreeDepth2, REPTreeDepth2, and J48.0001, which would add approximately 12 milliseconds to the already existing 3 milliseconds of calculation time for the meta features in the mean, which seems reasonable, and even on the large MNIST data set only represented 8.5 minutes out of a computation time of almost five hours for the full set of meta features. An effect on the time required for and quality of predictions for other larger data sets would have to be examined still.

### 2018-03-14 Writing/Thesis/Tex/content/chapter-evaluation.tex
Create Presentation

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up to 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' [Reference Missing]. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% Implementation of measures
For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used [REFERENCE MISSING]. Regarding the Mann-Whitney U, the strategy for ties was set to averaging, and the NaNs were set to be removed before the analysis was started.

>>>>

% How base performance data generated
The performance data of the classifiers for the selected data sets was generated on a linux cluster with nodes consisting of two Intel(R) Xeon(R) E5-2670 processors running at 2.6GHz, 64GB RAM. For the computation of a single performance value of a classifier on a data set, two CPU cores and 16GB RAM were used, with a timeout of eight hours. Up to 150 of such processes were executed in parallel. For each of the classifiers, the predictive accuracy (the percentage of correctly classified instances in the data set) was recorded on each data set by means of five times stratified Monte-Carlo cross validation with a 70/30 split in training and test data. The stratified split was generated with the help of JAICore, `A Java library for infrastructural classes and basic algorithms in the area reasoning, search, and machine learning' \cite{jaicore}. When a timeout occurred or the evaluation failed otherwise, the predictive accuracy was set to zero.

@@

% Implementation of measures
For the computation of the Mann-Whitney U and Kendall rank correlation coefficient, Apache Commons implementations were used \cite{apache}. Regarding the Mann-Whitney U, the strategy for ties was set to averaging, and the NaNs were set to be removed before the analysis was started.

### 2018-03-14 Writing/Thesis/Tex/content/chapter-introduction.tex
Create Presentation

%% Context
% Need more automated analysis of data
The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized. In a white paper, the International Data Corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data only 3\% were tagged as to enable further processing, and only 0.5\% were analyzed \cite{gantz2012the}. A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}. While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available. This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and the process is not accessible enough to non-experts. It thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.

@@

%% Response
% Therefore the goal is testing the this assumption if possible by using regression algos and preference learning
Thus, the aim of this thesis is the implementation and evaluation of two different approaches to ranking classification algorithms based on past-performances of the algorithms and according to properties of the data set. The two approaches include one regression-based approach that breaks down the problem of predicting a ranking into predicting a single performance value for each algorithm and then ranking them accordingly, and a preference based approach that is concerned with learning the rankings directly. Especially in the case of regression based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.

@@

In order to conduct this evaluation, an implementation of the two approaches is needed. A third goal is thus the development of an AutoML-tool that, after a pre-processing phase, returns a ranking of classifiers for a given data set, using either regression- or preference models for the prediction. The pre-processing phase constitutes of recording classifier performances on a number of data sets together with properties of the data sets to serve as training data, and training the regression models or preference model respectively.

>>>>

%% Context
% Need more automated analysis of data
The potential of big data is evident, and an increasing amount of information is collected and available for analysis - but this potential is not utilized. In a white paper, the International Data Corporation claims that in 2012, out of the 2.8 zettabytes (ZB) of available data only 3\% were tagged as to enable further processing, and only 0.5\% were analyzed \cite{gantz2012the}. A follow-up paper in 2017 projects that in 2025, 15\% of the estimated 163 ZB of global data will be tagged, and approximately 3\% analyzed \cite{gantz2017data}. While this is more optimistic, it still shows that there is a huge gap between the amount of data that could potentially be used and the amount of data actually available. This indicates that the demand of data to be analyzed cannot be covered by data scientists alone, and the process is not accessible enough to non-experts. It thus calls for automation of the process in a way that not much expertise in the field of machine learning is needed to gain insights about the collected data.

@@

%% Response
% Therefore the goal is testing the this assumption if possible by using regression algos and preference learning
Thus, the aim of this thesis is the implementation and evaluation of two different approaches to ranking classification algorithms based on past-performances of the algorithms and according to properties of the data set. The two approaches include one regression-based approach that breaks down the problem of predicting a ranking into predicting a single performance value for each algorithm and then ranking them accordingly, and a preference based approach that is concerned with learning the rankings directly. Especially in the case of regression-based ranking there is reason to believe that such a prediction is possible, as regression models have been used successfully to predict the performance of an algorithm dependent on the hyperparameter configuration \cite{DBLP:conf/aaai/EggenspergerHHL15}.

@@

In order to conduct this evaluation, an implementation of the two approaches is needed. A third goal is thus the development of an AutoML-tool that, after a pre-processing phase, returns a ranking of classifiers for a given data set, using either regression or preference models for the prediction. The pre-processing phase constitutes of recording classifier performances on a number of data sets together with properties of the data sets to serve as training data, and training the regression models or preference model respectively.
